---
title: "RMarkdown demonstration"
author: "Finn Lindgren"
output:
  html_document:
    number_sections: yes
header-includes:
  - \newcommand{\bm}[1]{\boldsymbol{#1}}
  - \newcommand{\mat}[1]{\begin{bmatrix}#1\end{bmatrix}}
---

```{r setup, include = FALSE}
# Set default code chunk options
knitr::opts_chunk$set(
  echo = FALSE
)

suppressPackageStartupMessages(library(tidyverse))
theme_set(theme_bw())
```

# This is a heading

RMarkdown documents combine regular text with R _code chunks_, and
partial LaTeX equation support.

The following is an R code "chunk". Any output from running the code
will be typeset as well.

```{r}
cos(1)
```

We can include code from script files, optionally without showing it.
```{r external-code, code=readLines("my_code.R"), eval=TRUE}
```

The output of R code can also be included in lines of text, like
$\sin(1)=`r sin(1)`$. Note: RMarkdown is sometimes picky about
whitespace; in this example, eliminating whitespace and having the R
code start on a new line turned out to be the safest option.

## This is a sub-heading

This is some more text with a simple mathematical formula,
$y_i = \beta_0 + x_i \beta_1 + \epsilon_i$. The mathematical formula
syntax is essentially a subset of the powerful LaTeX notation. Larger
formulas can be "displayed", using `$$` instead of `$`. For example,
$$
y_i = \beta_0 + \sum_{k=1}^p X_{ik} \beta_k + \epsilon_i ,
$$
is displayed on a line of its own.

In matrix form, the equation can be written
$$
\bm{y} = \bm{X}\bm{\beta} + \bm{\epsilon} ,
$$
where
$$
\bm{X} = \mat{
1 & X_{11} & \dots & X_{1p} \\
\vdots & \vdots & \ddots & \vdots \\
1 & X_{n1} & \dots & X_{np}
}
$$


A blank line gives a new paragraph.

If we only want the result of a chunk of R code to be seen, we can add
special instructions in a comment at the beginning of the code chunk.
See <https://yihui.name/knitr/options/> for a list of all the available
options!

```{r echo=FALSE}
sin(1)
```

The `echo=FALSE` option can be useful for hiding code where we only want
to show the result of a computation, and note the code itself. Another
useful option is `eval=FALSE`, which can be used for chunks of code that
should be shown but not run, perhaps to illustrate a programming error,
which RMarkdown would otherwise complain about:

```{r echo=TRUE,eval=FALSE}
curve(cos x, 0, 1)
```

We can also include R generated figures:

```{r myplot, echo=FALSE}
ggplot(data.frame(x = seq(1e-3, pi, length.out = 1000)) %>%
         mutate(fun = cos(pi / x))) +
  geom_line(aes(x, fun))
```

# Code appendix

We can show (and optionally run) code from earlier code chunks:

```{r ref.label="myplot", echo=TRUE, eval=FALSE}
```
